Highcharter Handbook

### 2019-08-16 04_highcharter-handbook/highcharter-handbook.Rmd
2nd work comp

library(highcharter)
library(tidyverse)
library(forecast)
knitr::opts_chunk$set(echo = TRUE)
```

@@

`highcharter` is an R implementation of the highcharts javascript graphing API through R's `htmlwidgets`. Most of the highcharts functionality is implemented through `highcharter` however the documentation is somewhat limited. This guide will provide examples on how to create and customise various graphs whilst providing some tips on how to think about the package that will help you build and debug your charts. I'll try to show and explain (to the best of my knowledge) the most common graphs and customisation options I use in my day-to-day work.

Your most important resources should be the highcharter official website, and the highcharts api documentation which you should bookmark in your browser:

* [Highcharter official website](http://jkunst.com/highcharter/)
* [Highcharts API Documentation](https://api.highcharts.com/highcharts/)

@@

If your

@@

## hchart() + hcaes()

The most practical use of `hchart()` however is to use it like you would the `ggplot()` function. The implementation is slightly different - you have to specify your geom type inside the `hchart()` call for example - but the

```{r}
hchart(starwars, "column", hcaes(x = name, y = height))
```

There's a number of things you might notice about this chart if you've spent a bit of time graphing in R. First thing is that if you can interact with it; hover over it to see a (relatively ugly) tooltip. Second is that it's dynamic, which you'll notice initially because there are more bars (star wars characters) than there are labels on the y-axis. To see an exaggerated version of this reduce the width of your browser window to see the chart react and replot as it tries to estimate the best way to present the data without it looking busy and cluttered; the number of characters shown on the y-axis will keep decreasing.

>>>>

library(highcharter)
library(tidyverse)
library(forecast)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

@@

`highcharter` is an R implementation of the highcharts javascript graphing API through R's `htmlwidgets`. Most of the highcharts functionality is implemented through `highcharter` however the documentation is somewhat limited. This guide will provide examples on how to create and customise various graphs whilst providing some tips on how to think about the package that will help you build and debug your more ambitious charts. I'll try to show and explain (to the best of my knowledge) the most common graphs and customisation options I use in my day-to-day work.

Your most important resources should be the `highcharter` official website, and the highcharts api documentation which you should bookmark in your browser:

* [Highcharter Official Website](http://jkunst.com/highcharter/)
* [Highcharts API Documentation](https://api.highcharts.com/highcharts/)

@@

Most (~90%) of your day-to-day charts can be probably written with 2-3 lines of code using the `hchart` and `hcaes` functions. These functions allow you packages `ggplot` like syntax. That is if your

In `highcharter`, `ggplot`'s grammar of graphics aesthetic mapping is supported through the `hchart()` function.

A simple `ggplot` call might look like the following:

```{r message=FALSE, warning=FALSE}
ggplot(starwars, aes(x = name, y = height)) +
  geom_col()
```

This chart (let's be honest here) looks awful. For full disclosure `ggplot` has a number of functional advantages over highcharter as it has simple implementations of reasonably complex chart types. But highcharter creates quick, readable, nice looking default charts that can be presented in a usable publishing format (a html page) a thousand times better than ggplot.

Here's the highcharter version of this plot:

```{r message=FALSE, warning=FALSE}
hchart(starwars, "column", hcaes(x = name, y = height))
```

There's a number of things you might notice about this chart and how it differs from it's ggplot counterpart.

* 
* t thing is that if you can interact with it; hover over it to see a (relatively ugly) tooltip. Second is that it's dynamic, which you'll notice initially because there are more bars (star wars characters) than there are labels on the y-axis. To see an exaggerated version of this reduce the width of your browser window to see the chart react and replot as it tries to estimate the best way to present the data without it looking busy and cluttered; the number of characters shown on the y-axis will keep decreasing.

@@
